Resolvable Ambiguity

### 2019-07-10 paper/paper.tex
Fix labels of static and dynamic resolvability definitions

\begin{definition}[Completeness of Static Resolvability]
  A decision procedure $f$ solving the static resolvability problem is \emph{complete} iff

@@

% todo: improve label (where used?)
\begin{definition}[Soundness of Dynamic Resolvability]\label{def:dynamic-procedure}
  A decision procedure $f$ solving the dynamic resolvability problem is sound iff

@@

\begin{definition}[Completeness of Dynamic Resolvability]
  A decision procedure $f$ solving the dynamic resolvability problem is complete iff

>>>>

\begin{definition}[Completeness of Static Resolvability]\label{def:static-procedure-complete}
  A decision procedure $f$ solving the static resolvability problem is \emph{complete} iff

@@

\begin{definition}[Soundness of Dynamic Resolvability]\label{def:dynamic-procedure-sound}
  A decision procedure $f$ solving the dynamic resolvability problem is sound iff

@@

\begin{definition}[Completeness of Dynamic Resolvability]\label{def:dynamic-procedure-complete}
  A decision procedure $f$ solving the dynamic resolvability problem is complete iff
